---
title: "Final project of Developing Data Products"
author: "ZC"
date: "June 24, 2018"
output: ioslides_presentation
editor_options: 
  chunk_output_type: console
---

## R Markdown

- This is a presentation for the final Project of "Developing data products" couresea course
 - This course is part of the "Data Science specialization"
 - The project consists in two activities:
     - Create a Shiny application
     - Create a Reproducible Pitch Presentation
     
 - The shiny app developed for this assignment is avalilable at https://zcuidata.shinyapps.io/project_3/
 - The source codes of ui.R and server.R and also presentation are available on https://github.com/ZhenhuaCui/Final-project-of-Developing-Data-Products.git
 
```{r, include=FALSE}
library(plotly)
```

## Dataset examples
MPG shinyapp is based on R build-in mtcars dataset. A simple linear regression model is built within the app. 

```{r cars, echo = TRUE}
head(mtcars)
```

## Plot in Shiny app
The histogram generated on the right-hand side shows the distribution of MPG of cars in the dataset. The user inputs via fluidPage on the left-hand side will be passed to the model to predict MPG, which will be displayed under the histogram.
```{r, echo=FALSE}
hist(mtcars$mpg, xlab = "Miles Per Gallon",xlim = c(10, 35),breaks=20, main="Histogram of MPG")
```


## Thank you
Thanks for your time